Layered Grammar for Alluvial Plots

### 2020-01-20 paper.rmd
typo

Parallel sets plots might be viewed as a special subtype of Sankey diagram with the following features: Ribbons proceed monotonically along one dimension, and e very ribbon encounters a box at every axis. These graphical constraints correspond to combinatorial constraints on the data, which amount to a id--key--value structure in which every id--key pair takes exactly one value (possibly 0 or `NA`).
In this sense, the plots produced by the ggplot2 extensions (and by the alluvial package) are parallel sets plots: Cohorts are partitioned into categories at each axis and connected by ribbons whose widths encode their magnitudes.[^hammock]

>>>>

Parallel sets plots might be viewed as a special subtype of Sankey diagram with the following features: Ribbons proceed monotonically along one dimension, and every ribbon encounters a box at every axis. These graphical constraints correspond to combinatorial constraints on the data, which amount to a id--key--value structure in which every id--key pair takes exactly one value (possibly 0 or `NA`).
In this sense, the plots produced by the ggplot2 extensions (and by the alluvial package) are parallel sets plots: Cohorts are partitioned into categories at each axis and connected by ribbons whose widths encode their magnitudes.[^hammock]
